Periodograms for Multiband Astronomical Time Series

### 2015-01-25 writeup/paper.tex
add some tweaks and some references

The API for the module is largely influenced by that of the {\tt scikit-learn} package\footnote{\url{http://scikit-learn.org}} \citep{scikit-learn}, in which models are class objects which can be ``fit()`` to data.
Here is a basic example of how you can use the code to download data, fit a multiband model to the data, and compute the power at a few periods:

@@

# Compute power at the following periods
model.periodogram([0.2, 0.3, 0.4])
\end{lstlisting}

Other models are available as well. For example, here is how you can compute the periodogram under the supersmoother model:

@@

# Compute power at the following periods
model.periodogram([0.2, 0.3, 0.4])
\end{lstlisting}

The code contains many more methods, and much more functionality that what is shown here. For updates and more information, visit \url{http://github.com/jakevdp/multiband_LS}.

>>>>

The API for the module is largely influenced by that of the {\tt scikit-learn} package\footnote{\url{http://scikit-learn.org}} \citep{scikit-learn}, in which models are Python class objects which can be fit to data with the \texttt{fit()} method.
Here is a basic example of how you can use the package to download the data used in this paper, fit a multiband model to the data, and compute the power at a few periods:

@@

# Compute power at the following periods
periods = [0.2, 0.3, 0.4, 0.5] # periods in days
power = model.periodogram(periods)
\end{lstlisting}

Other models are available as well. For example, here is how you can compute the periodogram under the supersmoother model; this implementation of the supersmoother periodogram makes use of the \texttt{supersmoother} Python package \citep{Vanderplas2015}.

@@

# Compute power at the following periods
power = model.periodogram(periods)
\end{lstlisting}

The models in the \texttt{multiband\_LS} package contain many more methods, and much more functionality that what is shown here. For updates, more examples, and more information, visit \url{http://github.com/jakevdp/multiband_LS}.
